### 2022-11-14 NSF2022/Description/specificaim1v2.tex
proof reading

\section{Proposed Research}
\label{sec:proposed-work}

\subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
\label{sec:specificaim1}
We introduced \eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
existing methods for studing vesicles and bilayers. The simulation
results in (Figures~\ref{fig:JPv_linearshear} and~\ref{fig:JPv_rupture})
show that two-dimensional, granule-based vesicles replicate the
equilibria and hydrodynamics for continuous curves~\cite{FuQuRyYo22,
Fu2018_SIAM}. Our next goal is to study the model using rigorous
analysis and consider three-dimensionsional effects.

@@

\begin{wrapfigure}[12]{r}{0.5\textwidth}
  \vspace{-5pt}
  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-5pt}
  \caption{\label{fig:amphiphilic_assembly} Self-organization under
  amphiphilic boundary condition. (a) Granules first match hydrophobic
  tails (red), (b) then align length-wise. (c) The principle of
  self-organization holds in three dimensions as simulated by Kohl,
  Corona, and Veerapaneni~\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
Bending enters through the splay of the granule directors. In
Figure~\ref{fig:JPv_linearshear}, for example, the directors have
negative, respectively positive, splay $\nabla_{\Sigma} \cdot \dd$ in
the outer, respectively inner monolayers. Here $\nabla_{\Sigma}\cdot{} =
\nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$ is the surface
divergence for the outward unit surface normal $\NN$. From differential
geometry, we have that $\nabla\cdot \dd = \pm 2H$ whenever $\dd$ is
everywhere parallel to $\NN$, and this is how the curvature term arises
in equation~\eqref{eq:Canham-Helfrich}. For two-dimensional vesicles,
$H$ is replaced with the curvature $\kappa$ of the curve $\mathbf{C}$.
Granules are at rest when attraction balances repulsion, and will have
stretching when the distance between neighboring granules is increased
from rest.

PI Ryham has experience in the sharp interface analysis for phase field
formulations of elastic bending energy~\cite{0951-7715-18-3-016, Du05},
and topological indicators~\cite{DuEuler}, as well as for
Poisson-Boltzman equations~\cite{Lee2018, 1531-3492_2006_2_357}. Tools
for addressing Problem 2 have been developed for bulk nematic liquid
crystal potentials in the area of colloidal
homogenization~\cite{Canevari2019DesignOE, doi:10.1137/18M1163919,
doi:10.1137/18M1163919, BERLYAND200597, doi:10.1137/130910348}, and is
related to dimension reduction for curved nematics confined to thin
films~\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
doi:10.1142/S0218202516500470, FoFrLe07}. We start by assuming circular
granules aligned normally to the curve, and then generalize the problem
to account for aspect ratio of elliptical granules and nonzero tilt.

>>>>

\section{Proposed Research}
\label{sec:proposed-work}
The three specific aims of this proposal are
mathematical analysis of the system
and three-dimensional energies
(\S \ref{sec:specificaim1}: PI Ryham),
numerical implementation for large granule-number
and three dimensional suspensions
(\S \ref{sec:specificaim2}: PI Quaife),
and kinetic theory
(\S \ref{sec:specificaim3}: PI Young).
\subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
\label{sec:specificaim1}
We introduced \eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
existing methods for studing vesicles and bilayers. The simulation
results in (Figures~\ref{fig:JPv_linearshear} and~\ref{fig:JPv_rupture})
show that two-dimensional, granule-based vesicles replicate the
equilibria and hydrodynamics for continuous curves~\cite{FuQuRyYo22,
Fu2018_SIAM}. Our next goal is to study the model using rigorous
analysis and consider three-dimensionsional effects.

@@

\begin{wrapfigure}[11]{r}{0.5\textwidth}
  \vspace{-8pt}
  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:amphiphilic_assembly} \footnotesize
  Self-organization under amphiphilic boundary condition. (a) Granules
  first match hydrophobic tails (red), (b) then align length-wise. (c)
  The principle of self-organization holds in three dimensions as
  simulated by Kohl, Corona, and
  Veerapaneni~\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
Bending enters through the splay of the granule directors. In
Figure~\ref{fig:JPv_linearshear}, for example, the directors have
negative, respectively positive, splay $\nabla_{\Sigma} \cdot \dd$ in
the outer, respectively inner monolayers. Here $\nabla_{\Sigma}\cdot{} =
\nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$ is the surface
divergence for the outward unit surface normal $\NN$. From differential
geometry, we have that $\nabla\cdot \dd = \pm 2H$ whenever $\dd$ is
everywhere parallel to $\NN$, and this is how the curvature term arises
in equation~\eqref{eq:Canham-Helfrich}. For two-dimensional vesicles,
$H$ is replaced with the curvature $\kappa$ of the curve $\mathbf{C}$.
Granules are at rest when attraction balances repulsion, and will have
stretching when the distance between neighboring granules is increased
from rest.

PI Ryham has carried out sharp interface-limit analyses for phase field
formulations of elastic bending energy~\cite{0951-7715-18-3-016, Du05},
and topological indicators~\cite{DuEuler}, as well as for
Poisson-Boltzman equations~\cite{Lee2018, 1531-3492_2006_2_357}. Tools
for addressing Problem 2 have been developed for bulk nematic liquid
crystal potentials in the area of colloidal
homogenization~\cite{Canevari2019DesignOE, doi:10.1137/18M1163919,
doi:10.1137/18M1163919, BERLYAND200597, doi:10.1137/130910348}, and is
related to dimension reduction for curved nematics confined to thin
films~\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
doi:10.1142/S0218202516500470, FoFrLe07}. We start by assuming circular
granules aligned normally to the curve, and then generalize the problem
to account for aspect ratio of elliptical granules and nonzero tilt.
